### 2015-06-09 text/ms.Rmd
More edits to methods

$$
\hat{\theta} = \mathrm{argmin}_\theta(L(b \, | \, \hat{b}_{\mathrm{ensemble}}))
$$

$$
\hat{b}_\mathrm{ensemble} = 
f(\hat{b}_\mathrm{CMSY}, \hat{b}_\mathrm{COM-SIR}, 
\hat{b}_\mathrm{SSCOM}, \hat{b}_\mathrm{mPRM}, 
S(0.2), S(0.5), | \, \theta)
$$

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from COM-SIR,
$\hat{b}_\mathrm{COM-SIR}$ etc., $b$ is the true value the model is fitted to,
$S(n)$ represents the spectral density at frequency $n$ of the scaled catch
series, and $\theta$ is the set of parameters for the regression function.

<!--
*Linear model*: For populations $i$ $1$ through $n$, individual models and
covariates $j$ $1$ through $m$, and allowing $\theta$ to refer to both
quantities estimated from individual models and additional covariates, we fit
the linear model with two-way interactions as:
-->

<!--\noindent-->
<!--The geometric mean is calculated as-->
<!--$$B/B_{\mathrm{MSY-ensemble}(i)} = \exp \left(\frac{\sum_{j=1}^{4} \log B/B_{\mathrm{MSY}(ji)}}{4}\right)$$-->

<!--$$-->
<!--\log B/B_{\mathrm{MSY-ensemble}(i)} = -->
  <!--\beta_0 + \beta_1 \log B/B_{\mathrm{MSY}(i)} -->
<!--$$-->

<!--
\begin{equation}
\theta_{\mathrm{ensemble}(i)} = 
  \beta_0 + 
  \sum_{j=1}^m \beta_j \theta_{j(i)} + 
  \sum_{j=1}^m \sum_{\substack{k =1 \\ j \neq k}}^m 
            \beta_{kj} \theta_{k(i)} \theta_{j(i)} +
  \epsilon_i, \quad
  \epsilon_i \sim \mathrm{Normal}(0, \sigma),
\end{equation}

\noindent
where the $\beta$ represent coefficients and $\epsilon$ represents normally
distributed residual variation. We also tried fitting linear models without
interactions but found better cross-validation predictive performance from all
performance measures evaluated using the procedure outlined below.
-->

*Random forests* are a machine learning method that combines a series of
regression trees. Regression trees sequentially determine what value of a
predictor best splits the response data into two 'branches' based on a
specified loss function. In random forests, a series of regression trees are
built on a random subset of the data and random subset of the covariates of the
model. By combining many of these stochastically generated models, random
forests can provide strong predictive performance and fit highly non-linear
relationships (REFs). We fit random forest models with the **randomForest**
package [@liaw2002] for \textsf{R} with the default argument values.

*Boosted regression models* are a machine learning method that, like random
forests, combines a series of regression trees built on random subsets of the
data, but also add a boosting procedure. Boosting refers to fitting a series of
models with each subsequent model fit to the residuals from the previous model;
data points that are fit poorly in a given model are given more weight in the
next model [@elith2008]. Boosting can result in TODO and TODO and is a common
and powerful machine learning technique [@elith2008]. We fit boosted regression
tree models with the **GBM** package [@ridgeway2015] for \textsf{R}. Based on
cross-validation with the **caret** package (Supporting Materials, Fig. SX), we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.

For all ensemble models of mean \bbmsy\\, which is bounded at zero, we fit the
models in log space and exponentiated the predictions to derive a median
estimate of \bbmsy\\. For the estimates of \bbmsy\\ slope, which are not
bounded at zero, we fit ensemble models on the natural untransformed scale.

>>>>

$$
\hat{\theta} = 
\mathrm{argmin}_\theta \left( L(b \, | \, \hat{b}_{\mathrm{ensemble}}) \right)
$$
$$
\hat{b}_\mathrm{ensemble} = 
f \left( \hat{b}_\mathrm{CMSY}, \hat{b}_\mathrm{COM-SIR}, 
\hat{b}_\mathrm{SSCOM}, \hat{b}_\mathrm{mPRM}, 
S(0.2), S(0.5), | \, \theta \right)
$$

\noindent where $L$ is a generalized loss function, $f$ is some generalized
regression function, $\hat{b}_\mathrm{CMSY}$ is the prediction from the CMSY
model etc., $b$ is the true value the model is fitted to, $S(n)$ represents the
spectral density at frequency $n$ of the scaled catch series, and $\theta$ is
the set of parameters for the regression function. For all ensemble models of
mean \bbmsy\\, which is bounded at zero, we fit the models in log space and
exponentiated the predictions to derive a median estimate of \bbmsy\\. For the
estimates of \bbmsy\\ slope we fit ensemble models on the natural untransformed
scale.

We calculated the average ensemble models as the geometric mean of the
individual model median \bbmsy\\ estimates and the mean of the individual model
\bbmsy\\ slopes. We fit the linear model ensemble with second-order
interactions.

We fit two machine learning ensemble models based on regression trees.
Regression trees sequentially determine what value of a predictor best splits
the response data into two 'branches' based on a specified loss function. In
random forests, a series of regression trees are built on a random subset of
the data and random subset of the covariates of the model (REF). In generalized
boosted models (GBMs), each subsequent model is fit to the residuals from the
previous model; data points that are fit poorly in a given model are given more
weight in the next model [@elith2008]. Random forests and GBMs can provide
strong predictive performance and fit highly non-linear relationships (REFs).
We fit random forest models with the **randomForest** package [@liaw2002] for
\textsf{R} with the default argument values. We fit boosted regression tree
models with the **GBM** package [@ridgeway2015] for \textsf{R}. Based on
cross-validation with the **caret** package (Supporting Materials, Fig. SX), we
fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate
(shrinkage parameter) of $0.01$, and all other arguments at their default
values.
